---
title: "YOUR TITLE HERE"
author: "YOUR NAME HERE"
date: "TODAY'S DATE HERE"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Overview

*Describe the visualization you are creating at a broad overview level. What is the claim
you are trying to make with it? What kind of data are you working with? etc.*

## Dataset

*Your more detailed description of the dataset here. Where did it come from?
What processing has happened to the data before you got it? etc.*

```{r download-data}
# Remove this chunk if your data is small enough that you can just check it
# into the repo.

# If not, uncomment and edit the following lines appropriately:
# data_filename <- "data/data-file-name.csv" # or XLSX or whatever
# 
# if (!dir.exists("data"))
#   dir.create("data")
# if (!file.exists(data_filename)) {
#   download.file(url = "https://the-data-url-goes-here",
#                 destfile = data_filename)
# }
```


```{r load-data}
# your code to load the data here
```

*Describe the structure of the data--size, shape, level of granularity, etc.*

## Wrangling

*Describe, at a broad level, what you need to do to the data to make it into
the form you need for the graph.*

*Add code blocks, with appropriate names, for wrangling steps.*

## Visualization

*Vis code goes here*

## Analysis

*Analysis goes here.*
